Type Error Telemetry at Scale

### 2023-09-28 programming23/paper.tex
telemetry record fig
data asset -> data model, but both terms are useful
DM = roblox-specific thing
data asset = casual language, easier to make sense of in abstract + conclusion

%% TODO data assets ==> data model in rest of paper

@@

\begin{figure}[t]\centering
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline
    ID & Time & Mode & Reason & Size Info & Overall Counts & Edit Range Counts
    \\\toprule
  \end{tabular}
  \caption{Structure of a telemetry record. There are 13 overall counts and up to 70 edit range counts in each record.}
  \label{f:tdata}
\end{figure}

@@

On the object level, the analysis offers several lessons for the Luau
developers and other maintainers of gradually-typed languages:
\begin{itemize}
  \item
    Nearly all creators (\pct{90}) use the default ``no check''
    typechecking mode~(\cref{f:dataset-overview}).
    Since the next typing mode (\mnonstrict{}) requires no annotations and is
    very conservative about the errors it reports, we conjecture that
    developers would have no objections to using it and are simply unaware that
    other modes exist.
%  \item
%    \pct{50} of all errors are in current module, so probably errors appear locally (not in a distant module);
%    \pct{5} of (current? old??) type errors overlap with edit range, so they don't stick around.
  \item
    Creators tend to fix errors immediately rather than dealing with them in a batch
    or ignoring the errors altogether~(\cref{f:error-density,f:error-changes}).
    % Changes to the number of errors balance one another~(\cref{f:error-density});
    % edits are equally likely to add or remove errors~(\cref{f:error-changes}).
  \item
    All Luau scripts interact with data assets, but no typechecking mode
    has a precise view of the data.
    Improving precision is an important direction for future work.
    Until then, \mstrict{} mode clearly needs to relax its data-asset
    analysis because it raises even more errors than \FS{} checking~(\cref{f:tefs-compass}).
\end{itemize}

>>>>

@@

\begin{figure}[t]\centering
  \begin{tabular}{|l|l|l|l|l|l|l|}\hline
    ID & Time & Mode & Reason & Size Info & Overall Counts & Edit Range Counts
    \\\toprule
    \multicolumn{6}{c}{\upbracefill} & \multicolumn{1}{c}{\upbracefill} \\[-0.5ex]
    \multicolumn{6}{c}{fixed-size} & \multicolumn{1}{c}{variable-size}
  \end{tabular}
  \caption{Structure of a telemetry record. There are 13 overall counts and up to 70 edit range counts in each record.}
  \label{f:tdata}
\end{figure}

@@

On the object level, the analysis offers several lessons for the Luau
developers and other maintainers of gradually-typed languages:
\begin{itemize}
  \item
    Nearly all creators (\pct{90}) use the default ``no check''
    typechecking mode~(\cref{f:dataset-overview}).
    Since the next typing mode (\mnonstrict{}) requires no annotations and is
    very conservative about the errors it reports, we conjecture that
    developers would have no objections to using it and are simply unaware that
    other modes exist.
%  \item
%    \pct{50} of all errors are in current module, so probably errors appear locally (not in a distant module);
%    \pct{5} of (current? old??) type errors overlap with edit range, so they don't stick around.
  \item
    Creators tend to fix errors immediately rather than dealing with them in a batch
    or ignoring the errors altogether~(\cref{f:error-density,f:error-changes}).
    % Changes to the number of errors balance one another~(\cref{f:error-density});
    % edits are equally likely to add or remove errors~(\cref{f:error-changes}).
  \item
    All Luau scripts interact with data assets, but no typechecking mode
    has a precise view of the data.
    Improving precision is an important direction for future work.
    Until then, \mstrict{} mode clearly needs to relax its data model
    analysis because it raises even more errors than \FS{} checking~(\cref{f:tefs-compass}).
\end{itemize}
